Placeholder title: Formal methods in constraint-based learning

### 2024-01-10 ITP draft/draft_lipics.tex
sime comments on the Intro

@@

Using Interactive Theorem Provers (ITPs) in combination with machine learning (ML) is a very new approach dating only a few years back CITE. 
The integration of formal methods with machine learning poses many challenges, stemming from the inherent differences between the two domains, from the black-box nature of many ML models, through scalability issues especially in the case of neural networks (NNs) to the lack of well-defined specifications required in formal methods.

>>>>

\usepackage[textwidth=2.5cm,textsize=footnotesize,colorinlistoftodos]{todonotes}
\newcommand{\knote}[2][]{\todo[inline,color=blue!10,#1]{KATYA: #2}}

@@

Using Interactive Theorem Provers (ITPs) in combination with machine learning (ML)
\knote{``in combination" is too broad; as there were works using Ml to speed up proofs. You only want to discuss using ITP in formalisation of ML/probabilistic reasoning}
 is a very new approach dating only a few years back CITE.
 \knote{``new" is to weak, new does not mean useful. So, probably the first sentence should start with motivating why it is a good idea to formalise these things in ITP} 
The integration of formal methods with machine learning poses many challenges, 
\knote{This changes focus from ITP to formal methods -- do you really need this?}
stemming from the inherent differences between the two domains, from the black-box nature of many ML models, through scalability issues especially in the case of neural networks (NNs) to the lack of well-defined specifications required in formal methods.

\knote{I don't know... There are choices how to start, but generally, we start with an idea that is well accepted by the community we address to a problem that we assume the audience will accept as interesting.}
\knote{For this reason, I would go as follows}
\knote{Formalisation of mathematics has been one of major research topics within the Interactive Theorem Proving (ITP) communities, from early successes in formaisation of the Kepler conjecture~\cite{}, to Four-colour theorem~\cite{}, Odd-Order Theorem~\cite{} and more recently, to consolidated efforts to create comprehensive mathematical libraries in Coq (Mathematical Components~\cite{}) and Lean (lookup names ~\cite{}). As statistical machine learning rests on differentiation, probability theory and linear algebra, it was only a matter of time to ask whether there is a strong case for, or specific interest in, formalising machine learning in ITP. The first attempt at ITP formalisation of neural networks was made by~\cite{bagnall2019certifying}, shortly followed by analysis 
of different perceptron forms in \cite{de2022use}, both in Coq. In both cases the formalisation aimed at
verifying abstract properties of neural networks: generalisation bounds in ~\cite{bagnall2019certifying} and various forms of convergent behaviour in \cite{de2022use}.  
More recent Coq formalisations, e.g. by \cite{AleksandrovV23} target proofs of theoretical properties of neural networks seen as functions. Say something about work of Alessandro? someone in Lean? someone in Isabelle?}
\knote{That was idea 1. General introduction}
\knote{Idea 2: you need to bring here some motivation why someone wants to study/formalise DL... I'd try to explain general motivation, without formally defining loss functions... (because defining loss functions implies defining neural nets as well, and you loose the point}
